A quantitative framework for investigating the reliability of network construction

### 2018-06-05 manuscript/CI_interactions.tex
less than 200 words too many now

  To progressively dissect the different contributions to uncertainty, we will start by considering how we could naively quantify interaction probability and its associated uncertainty \emph{for an interaction that has not yet been observed}. We consider the case where a pair of species have been observed co-occurring $n$ times, of which they have been observed to interact in $k = 0$ cases. We now aim to evaluate the uncertainty of this interaction. We consider the occurrence of an interaction as a Bernoulli trial. Consequently, the number of successes $k$ over $n$ trials will follow a binomial distribution:

@@

  The variance of a Bernoulli experiment is $n\lambda$(1-$\lambda$). It is important to remember that this variance describes the variability of the number of successes $k$ for $n$ trials and is not the variance associated with the estimation of $\lambda$. Given this variance, it is possible to compute the confidence interval for the MLE of $\lambda$ using any of several methods, including the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull interval} (for details, see [\citealp{Brown2001}]). Finding this estimate is therefore quite straightforward, but it nonetheless has two drawbacks. First, $\lambda$ is not a single point estimate but rather a random variable with an unknown distribution. This means that if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact. Rather, $k = 0$ implies that `no interaction' is the most likely outcome when the species do co-occur but there is nonetheless a substantial chance that the two species \emph{could} interact. In the situation where $k>0$, in contrast, we are sure that the interaction is feasible ($L = 1$) but still cannot be sure of the cause if the interaction is not observed at some sites/times (i.e., we cannot say why $k<n$). There may be local constraints ($X=0$) or we might simply not observe the interaction in every sample ($D<1$).

  Second, where the number of samples $n$ is very low (some pairs of species may never have been documented as co-occurring), there will be considerable uncertainty around our estimate of $\lambda$. In Fig.~\ref{upper_limits} and Box 2, we derive the Clopper-Pearson interval to explore how the estimate of $\lambda$ varies with sample size. At a small sample size, the 95\% confidence interval spans all values of $\lambda$. To establish that species are not interacting with any acceptable certainty requires tens of observations of the two species co-occurring but not interacting. As most data sets will lack such extensive sampling across all species pairs, we can use a Bayesian approach to supplement what data we do have with other sources of information.

@@

      \noindent where the function $B$ is the beta function. The posterior distribution of $\lambda$ therefore follows the beta distribution with new parameters $\alpha'= \alpha+k$ and $\beta'=\beta+n-k$. The weight of the prior on the posterior distribution can be understood from these parameter definitions: the difference between the posterior and the prior will increase with $k$ and $n-k$. In other words, the distribution of $\lambda$ for better-sampled pairs of species will rely less on the information used to build the prior distribution and depend more on the observed data.
      When plotted, we find the shape of the distribution gets narrower with $k$ and $n$ (Fig.~\ref{Salix_pdfs}).

@@

      Parameters $\alpha$ and $\beta$ determine the shape of the prior distribution, which follows a beta distribution. These are called hyper parameters. Below we identify four ways to formulate the prior distribution of $\lambda$.

      \subsubsection*{Uninformative prior}

          In the absence of any external information, an uninformative prior is the most conservative hypothesis for the distribution of $\lambda$. The beta distribution is in this case a uniform distribution, specified with hyper parameters $\alpha=1$ and $\beta=1$.

      \subsubsection*{Distribution of connectance}

          The ecological network literature boasts a collection of networks for which connectance has been calculated and for which we can thus define the connectance distribution. Connectance is measured as $C = L/S^2$, where $L$ is the number of interactions and $S$ is the number of species. It measures the filling of an interaction matrix and thereby expresses the average probability that any two species interact with each other. If we know only the mean $\overline{C}$ and the variance $\sigma_C^2$ of the distribution of $C$,          then the beta parameters could be computed as follows using the method of moments:

          \begin{equation}
          \alpha = \overline{C}(\frac{\overline{C}(1-\overline{C})}{\sigma_C^2}-1) ,
          \end{equation}

          \begin{equation}
          \beta = (1-\overline{C})(\frac{\overline{C}(1-\overline{C})}{\sigma_C^2}-1) .
          \end{equation}

      \subsubsection*{Degree distribution or interaction probabilities}

          The degree of a node in a network is defined as its number of connections to other nodes. The degree distribution of a network is then the probability distribution of these degrees over the whole network and the standardised degree could therefore be interpreted as an interaction probability. It is consequently possible to use the degree distribution to inform the prior distribution. The degree distribution could come from several networks, from a similar network (e.g. a known network at slightly different location) or from the network of interest if interaction probabilities for some species are already documented. The latter approach allows researchers to apply information from known, abundant species to the rarest species for which interactions are less frequently documented.

          If our focal network describes a system similar to that in a known network, we can use the distribution of interaction probabilities in that network to inform our prior. The probability of any interaction $L_{ij}$ depends on the degrees of species $i$ and $j$. Using normalised degrees $\Delta_i$ and $\Delta_j$ (i.e., degrees divided by the number of species in the network), we can obtain the probability of interaction $L_{ij}$=$\Delta_i\times\Delta_j$. Similar to the procedure for degree distribution, the distribution of these interaction probabilities can be used to establish a prior distribution before any data from the focal network are collected. For distributions of either degrees or interaction probabilities, the procedure for the estimation of the hyper parameters follows the same approach as described above for connectance except that each measurement is at the individual interaction level instead of the network level.

      \subsubsection*{Trait-matching function}

          As a fourth and final approach, it may be possible to obtain the prior distribution of $\lambda$ using the outcome of a trait-matching model, provided such a model has been parameterised using external data and relevant traits are available. In such a case, the prior distribution would follow the function $P(\lambda|\mathbf{T})=f(\mathbf{T})$ based on a set of traits for both species $\mathbf{T}$. There are several techniques available to perform this inference of interaction probability, some of which are Bayesian, and we refer to~\citet{Bartomeus2016} and~\citet{Weinstein2017} for recent reviews about this topic. Note that in this case the prior might not be beta-distributed and numerical methods might be required to compute the posterior distribution.

\section*{A quantitative example}

  The Bayesian framework can be illustrated with a simple quantitative example. Suppose we have $n = 10$ observations of co-occurrence between species $i$ and species $j$ in a given time interval and area, and $k = 3$ observations of interactions. The maximum likelihood estimate of the interaction probability is simply $\lambda_{MLE} = 3/10 = 0.3$.

  Now consider we know that species $i$ is known to interact with 10 species (other than species $j$), which have the following degrees:

    \vspace{12pt}
    \noindent\emph{
      degree=c(14, 4, 2, 3, 17, 6, 2, 15, 1, 1)
        }.
      \vspace{12pt}

    If the network has 20 species total, this gives the normalised degrees:

    \vspace{12pt}
    \noindent\emph{
      norm\_degree=c(0.65, 0.20, 0.10, 0.15, 0.85, 0.30, 0.10, 0.75, 0.05, 0.05)}.
      \vspace{12pt}

    Species $i$ has a normalised degree of 0.55 (it interacts with species $j$ and 10 other species). We can combine the normalised degree of $i$ with the normalised degrees of its interaction partners to obtain the following set of interaction probabilities for species $i$ and each of its interaction partners:

    \vspace{12pt}
    \noindent\emph{
       int\_probs = c(0.358, 0.110, 0.055, 0.082, 0.468, 0.165, 0.055, 0.412, 0.028, 0.028) }.
      \vspace{12pt}

    The mean of these interaction probabilities is 0.176, approximately two-thirds the $\lambda_{MLE}$ obtained from the observed data. We can use the distribution of these interaction probabilities as our prior distribution and estimate the uncertainty surrounding our $\lambda_{MLE}$. With some simple R code (function ``calculate\_parameters", \emph{Appendix S1}), we obtain prior parameters $\alpha$=0.998 and $\beta$=4.63. Using these priors in equations~\ref{mean} and~\ref{variance} above (or in the R function ``calculate\_distribution" in \emph{Appendix S1}), we find a prior $\bar\lambda$=0.177 and var($\lambda$)=0.026. Adding the observed data ($n=10$, $k=3$) and using the same code, we obtain posterior parameters $\alpha'$=4.00 and $\beta'$=11.6 and a posterior $\bar\lambda$=0.256 and var($\lambda$)=0.012. Comparing the posterior distribution to the prior, we see that the posterior is closer to the observed data and that the additional data about interactions between species $i$ and $j$ has reduced the variance. We may also wish to calculate a credible interval (analogous to the frequentist confidence interval). This is also quite straightforward in R (see function ``credible\_interval" in \emph{Appendix S1}). In this case, a 95\% credible interval for $\bar\lambda$ is (0.080, 0.491).

    Now, consider the case where the two species have never been observed interacting across $n$ trials, i-e. $k=0$. The question is then ``what is the probability that these two species do not interact''? Since it is not possible to prove that the two species could never interact (strictly speaking, in a Bayesian approach $\lambda=0$ is impossible), we must fix a threshold below which we consider that there is no interaction ($\lambda \sim 0$). We call this threshold probability $\lambda*$. We then use the cumulative distribution function to estimate $P(\lambda<\lambda*|L=0,n)$ for different $n$. The function ``samples\_for\_threshold" in \emph{Appendix S1} calculates distribution function for $\lambda*$ with an increasing number of trials. This yields a surprising result: it requires \textgreater24 observations of no interactions to be 95\% sure that the interaction probability is smaller than $\lambda*$=0.1 (recall Fig.~\ref{upper_limits}, Box 2). Note the special case where there is no observation of the two species co-occurring, $n = 0$.  In this situation, the posterior distribution converges to the prior distribution since the data include no information on the probability with which species might interact should they co-occur.

@@

    In the following section, we will provide an empirical example based on the well-sampled system of \emph{Salix}  plants, herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}; see Box 1 or \emph{Appendix S2} for a description). Using this dataset, we will demonstrate the derivation of prior distributions for the \emph{Salix}-galler and galler-natural enemy components of these networks and the differences between these priors and posterior distributions which include all information available in this dataset~\citep{Kopelke2017}. Finally, we will calculate network properties using a suite of networks sampled from these posterior distributions and show how the uncertainty around interactions that have not been observed impact these metrics.

  \subsection*{Computing the posterior distribution}

@@

      To obtain the priors based on the Zillis sub-network, we estimated frequencies of \emph{Salix}-galler interactions based on the normalised degree of each species in each network component (see \emph{Appendix S3} for details and code). Specifically, we obtained prior parameters of $\alpha$=8.72, $\beta$=305 for the \emph{Salix}-galler component and $\alpha$=0.700, $\beta$=8.49 for the galler-natural enemy components of the network. After calculating these prior parameters, we were then able to estimate the posterior distribution of interaction probabilities given the additional information in our dataset.

      For species where no co-occurrences were observed ($n=0$), we can calculate the estimates for the mean and variance of $\lambda_{ij}$ directly from the prior parameters following equations~\ref{mean} and~\ref{variance} (see \emph{Appendix S1} for R implementation). For the \emph{Salix}-galler network, the prior distribution  was: $\bar\lambda$=0.028, var($\lambda$)=8.60$\times$10$^{-5}$. The prior distribution for the galler-natural enemy network was: $\bar\lambda$=0.076, var($\lambda$)=0.008. The posterior interaction probabilities obtained based on the Zillis sub-network were much lower than those obtained based on~\citet[Data available from the Dryad Digital Repository: https://doi.org/10.5061/dryad.g7805]{Barbour2016}; this emphasises the importance of using an appropriate study system when constructing a prior (\emph{Appendix S4}).

      For a pair of species with some observed co-occurrences ($n>0$), we can update the prior distribution with these data. If we consider only pairs of species which were observed to co-occur but not to interact, $k_{ij}$ is always 0 and only $n_{ij}$ will vary between species pairs, giving $\alpha'$=$\alpha$ and $\beta'$=$\beta + n_{ij}$. As the most extreme case, consider a pair of species which co-occurred at all 374 sites and was never observed to interact. Using the priors described above, our distribution for the \emph{Salix}-galler network would become $\bar\lambda_{ij}$=1.27 $\times$ 10$^{-2}$, var($\lambda_{ij}$)=1.82 $\times$ 10$^{-5}$ while our distribution for the galler-natural enemy network would become $\bar\lambda_{ij}$=1.83 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=4.76. Distributions for both network components were very close to 0 with small variance about our estimate of $\lambda$; species $i$ and $j$ are extremely unlikely to interact at sites or times not included in our sample.

      For most pairs of species $i$ and $j$, however, $n_{ij}$ was much less than 374 and our posterior mean and variance therefore retain more of the influence of the prior. We can see this in the increasing means and variances as we decrease $n_{ij}$ (Fig.~\ref{Salix_pdfs}). The change in distribution as $n_{ij}$ decreases can also be shown  by calculating 95\% credible intervals for $\lambda$ (see the function ``credible\_interval" in \emph{Appendix S2}). The 95\% credible interval around the estimate of $\lambda$ also widens as $n_{ij}$ decreases from (0.001, 0.017) and (\textless0.001, 0.11) for hypothetical \emph{Salix}-galler and galler-natural enemy pairs that might be observed co-occurring at all 374 sites without any observed interaction to (0.152, 0.931) and (0.008, 0.364) for \emph{Salix}-galler and galler-natural enemy pairs that were never observed co-occurring. The 95\% credible interval for hypothetical \emph{Salix}-galler pairs widened from (0.006, 0.022) if the pair co-occurred at all sites to (0.013, 0.049) if they co-occurred at none. The 95\% credible interval for hypothetical galler-natural enemy pairs, meanwhile, widened from (0.00001, 0.008) to (0.0005, 0.304).

@@

      Rather than calculating credible intervals for a posterior distribution after collecting data, we may wish to know how many data points are necessary to obtain a given level of confidence that two co-occurring species do not interact. The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact (Fig.~\ref{Salix_cdfs}; see function samples\_for\_threshold in~\emph{Appendix S1}). In our dataset, the entire 95\% credible interval was (0.013, 0.049). We may therefore be 95\% confident that the interaction probability for \emph{Salix} and galler species that have not been observed co-occurring is below 0.05. As the peak of the prior distribution for the probability of interaction between \emph{Salix} and galler probabilities is around 0.02 (Fig.~\ref{Salix_pdfs}), to be 95\% confident that the interaction probability for these species is below 0.01 would require 1029 observed co-occurrences with no interaction - far more than the number of sites in the~\citep{Kopelke2017} dataset.

      The number of samples required to be 95\% confident that the interaction probability between galler and natural enemy species is below a threshold also increases quickly as the threshold decreases. The 95\% credible interval is (\textless0.001, 0.303) for the probability of interaction between two species observed to co-occur but never interact. To be 95\% confident that the probability of interaction is below 0.1, 0.05, or 0.01 would require 15, 39, and 229 observed co-occurrences, respectively.

@@

    It is fairly straightforward to compute most network metrics when the different $\lambda$ of the adjacency matrix are known and assumed not to vary without variance~\citep{Poisot2016}. Several of these metrics derive directly from quantitative indices of network structure which are equivalent to $\lambda$. The remainder, originally defined for binary networks, can be adjusted to account for interaction probabilities between zero and one. It is not as easy, however, to understand how the uncertainty in these estimated interaction probabilities influences network metrics. Computation of these metrics involves non-linear functions. Since Jensen's inequality states that the average of a non-linear function of a stochastic variable differs from the function of the average of that variable, any uncertainty in the values of $\lambda$ could bias both the mean and variance of a network metric. One way to avoid potentially biased analytical calculation of network properties is to calculate the properties of a suite of simulated networks.

    Using the prior distributions and procedures described above, we calculated posterior probability distributions for \emph{Salix}-galler or galler-natural enemy pairs that were not observed interacting. Using these posterior distributions and assuming probabilities of 1 for pairs of species that were observed interacting, we created a suite of 100 webs of each network type by randomly sampling from each posterior distribution. After obtaining these posterior networks, we calculated the connectance of each web, as well as the number of links per resource (\emph{Salix} in the \emph{Salix}-galler networks or galler in the galler-natural enemy networks) and links per consumer. To demonstrate how these network metrics will be affected by detection uncertainty, we then created a suite of filtered networks for each posterior network. Networks were filtered by randomly sampling 99\%, 95\%, 90\%, 80\%, 70\%, 60\%, and 50\% of the interactions included in each posterior network. This gradient is akin to a gradient of sampling effort. For each level of detection accuracy, we created 100 randomly-sampled networks per posterior-probability network (giving 100 posterior networks and 1000 detection-filtered networks each for the \emph{Salix}-galler and galler-natural enemy networks). We then calculated the same network properties as described above.

    We find, perhaps not surprisingly, that the posterior webs for the Salix-galler network  had higher connectances than the original, observed web (C=0.028 for the observed web and 0.082 $\leq$ C $\leq$ 0.096 for the posterior webs; Fig.~\ref{posterior_webs}A). The number of links per \emph{Salix} species in the observed web ($L_{\emph{Salix}}$=2.71) was similar to those in the posterior webs (2.53 $\leq L_{\emph{Salix}} \leq$ 3.19; Fig~\ref{posterior_webs}C). The number of links per galler, however, was lower in the observed web ($L_{galler}$=1.47) than in the posterior webs, accounting for the increased connectance (4.67 $\leq L_{galler} \leq$ 5.88; Fig.~\ref{posterior_webs}E). There was a more substantial difference in the nestedness of the observed and posterior webs: the observed network had NODF=0.560 while the posterior networks were more nested (1.39 $\leq NODF \leq$ 1.94). Even the networks sampled with a detection filter of 50\% had non-zero nestedness (Fig.~\ref{posterior_webs}G). This last result highlights the potential for the possibility for network structure to vary when considering the possibility that unobserved species pairs may interact.

    Considering the galler-natural enemy networks, the connectance, mean links per galler, and mean links per natural enemy were also much lower in the observed web (C=0.078, $L_{galler}$=9.99, and $L_{natural enemy}$=7.45, respectively) than in the posterior webs (0.186 $\leq$ C $\leq$ 0.198, 13.4 $\leq L_{galler} \leq$ 14.6, and 23.4 $\leq L_{natural enemy} \leq$ 25.0). When the detection probability was relatively low (i.e., 50\%), however, the properties of randomised networks became similar to those in the observed webs (Fig.~\ref{posterior_webs}B,D,F). Nestedness was higher in the observed network (NODF=6.85) than in the posterior webs (6.31 $\leq NODF \leq$ 6.82; Fig.~\ref{posterior_webs}H); in this case, the stronger the detection filter the farther apart were the observed and posterior webs.

@@

\begin{fullbox}{}
  \begin{spacing}{1.0}
    \textbf{Box 1: }\emph{Salix}-galler-natural enemy dataset.\\
    \indent As a case study, we use an extensively sampled \emph{Salix}-galler-natural enemy meta-network. This dataset consists of a single community type sampled across Europe: willow (\emph{Salix}) species, willow-galling sawflies, and their natural enemies. The data were collected over 29 years at 374 unique locations across Europe with a total of 641 site visits. Each site visit or each unique site can be considered as a network in its own right or as an independent sample from which to build the meta-network. Here we take the more conservative approach and pool visits to the same site for a sample size of 374 sub-networks. The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes. The high spatiotemporal resolution of this network and the unusually high sampling effort implemented at the site level makes this dataset particularly well suited for illustrating the difficulties in completely sampling a network and testing Bayesian approaches to overcome these difficulties.\\
    \indent We may begin by comparing the frequency of co-occurrences for pairs of species in each part of the network to reveal the challenge of having sufficient sampling to be confident that an interaction does not occur. Most pairs of species (3,986/4,992 \emph{Salix}-galler pairs and  9,794/12,096 galler-natural enemy pairs) are never found co-occurring and, for species that did occur together, the total number of co-occurrences was generally low (mean=4.24, variance=36.3 for \emph{Salix}-galler pairs; mean=3.87, variance=28.8 for galler-natural enemy pairs; Fig.~\ref{histograms}A-B). The bulk of these co-occurring species pairs were never observed to interact: only 2.82\% of \emph{Salix}-galler pairs and 7.76\% of galler-natural enemy pairs were observed interacting at one or more sites. Of those pairs that did interact, the incidence of interaction was also low (mean=12.0, variance=155 for \emph{Salix}-galler pairs; mean=4.04, variance=29.3 for galler-natural enemy pairs; Fig.~\ref{histograms}C-D). Thus, even in the most extensive data set that we could find, there was very little empirical data for each species pair. This suggests that limited sampling is a major source of uncertainty in all empirical networks. This dataset also illustrates the potential for increased sampling to not necessarily reveal more interactions as a pair of species that is able to interact may not be observed interacting in all samples where the pair co-occurs (Fig.~\ref{histograms}E-F).
  \end{spacing}
\end{fullbox}

@@

\begin{fullbox}{}
    \begin{spacing}{1.0}
    \textbf{Box 2: }Calculating the credible interval around a probability estimate\\
  \indent Here we describe the derivation of the Clopper-Pearson credible interval for the estimated probability of interaction $\lambda$ of a pair of species observed co-occurring $n$ times and interacting $k$ times. As we are most interested in the probability of interaction between species pairs that have never been observed co-occurring, we consider only the case where $k=0$ over a variety of $n$. This is straightforward to do in R (see the function ``credible\_interval" in \emph{Appendix S1}).

  First, we must obtain the $\alpha$ and $\beta$ parameters for the prior distribution. In this study we obtained these parameters using the R~\citep{R} function fitdist from the package fitdistrplus~\citep{fitdistrplus}. Once $\alpha$ and $\beta$ are known, we can update them using our observed data. Specifically, we are interested in $\alpha'=\alpha+k$ and $\beta'=\beta+n-k$. These parameters can then be used to calculate a credible interval using the R~\citep{R} function qbeta. In the table below, we present the 95\% credible intervals for \emph{Salix}-galler and galler-natural enemy pairs with different numbers of observed co-occurrences ($n$) and no observed interactions ($k=0$), calculated using prior information derived from the Zillis sub-network~\citep{Kopelke2017}.

>>>>

  We will start by considering how we could naively quantify interaction probability and its associated uncertainty \emph{for an interaction that has not yet been observed}. Consider the case where a pair of species have been observed co-occurring $n$ times, of which they have been observed to interact in $k = 0$ cases. To evaluate the uncertainty of this interaction, consider the occurrence of an interaction as a Bernoulli trial. In this framework, the number of successes $k$ over $n$ trials will follow a binomial distribution:

@@

  The variance of a Bernoulli experiment is $n\lambda$(1-$\lambda$). It is important to remember that this variance describes the variability of the number of successes $k$ for $n$ trials and is not the variance associated with the estimation of $\lambda$. Given this variance, it is possible to compute the confidence interval for the MLE of $\lambda$ using any of several methods, including the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull interval} (for details, see [\citealp{Brown2001}]). Finding this estimate is therefore quite straightforward. Importantly, $\lambda$ is not a single point estimate but rather a random variable with an unknown distribution. This means that if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact. Rather, $k = 0$ implies that `no interaction' is the most likely outcome when the species do co-occur but there is nonetheless some chance that the two species \emph{could} interact. In the situation where $k>0$, in contrast, we are sure that the interaction is feasible ($L = 1$). If $n>k>0$, the interaction is feasible but there may be local constraints ($X=0$) or detection errors ($D<1$) causing the interaction not to be observed in some samples. % The non-point nature of lambda seems like a feature, not a bug.

  Treating $\lambda$ as a distribution does, however, have an important drawback. Where the number of samples $n$ is very low, as for rare species, there will be considerable uncertainty around our estimate of $\lambda$. In Fig.~\ref{upper_limits}, we derive the Clopper-Pearson interval to explore how the estimate of $\lambda$ varies with sample size. At a small sample size, the 95\% confidence interval spans all values of $\lambda$. To establish that species are not interacting with any acceptable certainty requires tens of observations of the two species co-occurring but not interacting. As most data sets will lack such extensive sampling across all species pairs, we can use a Bayesian approach to supplement the data we have with other sources of information.

@@

      \noindent where the function $B$ is the beta function. The posterior distribution of $\lambda$ therefore follows the beta distribution with new parameters $\alpha'= \alpha+k$ and $\beta'=\beta+n-k$. The weight of the prior on the posterior distribution can be understood from these parameter definitions: the difference between the posterior and the prior will increase with $k$ and $n-k$. In other words, the distribution of $\lambda$ for better-sampled pairs of species will rely less on the information used to build the prior distribution and depend more on the observed data.
      When plotted, we find the shape of the distribution gets narrower with $k$ and $n$ (Fig.~\ref{Salix_pdfs_cdfs}).

@@

      Parameters $\alpha$ and $\beta$ determine the shape of the prior distribution of $\lambda$, which follows a beta distribution. These are called hyper parameters. The prior may be chosen to be uninformative, if no external information is available, or may draw on information such as distributions of connectance across webs, degree within webs, or a trait-matching function (see \emph{Appendix S1} for details and a simple quantitative example).

@@

    In the following section, we will provide an empirical example based on the well-sampled system of \emph{Salix} plants, herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}; see Box 1 or \emph{Appendix S2} for a description). Using this dataset, we will demonstrate the derivation of prior distributions for the galler-natural enemy component of these networks (see \emph{Appendix S3} for the \emph{Salix}-galler component) and the differences between these priors and posterior distributions which include all information available in this dataset~\citep{Kopelke2017}. Finally, we will calculate network properties using a suite of networks sampled from these posterior distributions and show how the uncertainty around interactions that have not been observed impact these metrics.

  \subsection*{Computing the prior and posterior distributions}

@@

      To obtain the priors based on the Zillis sub-network, we estimated frequencies of interactions based on the normalised degree of each species in each network component
      (see \emph{Appendix S6} for details and code). Specifically, we obtained prior parameters of $\alpha$=0.700, $\beta$=8.49. After calculating these prior parameters, we were then able to estimate the posterior distribution of interaction probabilities given the additional information in our dataset.

      For species where no co-occurrences were observed ($n=0$), we can calculate the estimates for the mean and variance of $\lambda_{ij}$ directly from the prior parameters following equations~\ref{mean} and~\ref{variance} (see \emph{Appendix S7} for R implementation). For these interactions, we obtain $\bar\lambda$=0.076, var($\lambda$)=0.008. The posterior interaction probabilities obtained based on the Zillis sub-network were much lower than those obtained based on~\citet[Data available from the Dryad Digital Repository: https://doi.org/10.5061/dryad.g7805]{Barbour2016}; this emphasises the importance of using an appropriate study system when constructing a prior (\emph{Appendix S4}).

      For a pair of species with some observed co-occurrences ($n>0$), we can update the prior distribution with data. If we consider only pairs of species which were observed to co-occur but not to interact, $k_{ij}$ is always 0 and only $n_{ij}$ will vary between species pairs. This gives $\alpha'$=$\alpha$ and $\beta'$=$\beta + n_{ij}$. As the most extreme case, consider a pair of species which co-occurred at all 374 sites and was never observed to interact. Using the priors described above, our distribution would become $\bar\lambda_{ij}$=1.83 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=4.76. This distributions is very close to 0 with small variance about $\lambda$; species $i$ and $j$ are extremely unlikely to interact at sites or times not included in our sample.

      For most pairs of species $i$ and $j$, however, $n_{ij}$ was much less than 374 and our posterior mean and variance therefore retain more of the influence of the prior. We can see this in the increasing means and variances as we decrease $n_{ij}$ (Fig.~\ref{Salix_pdfs_cdfs}). The change in distribution as $n_{ij}$ decreases can also be shown  by calculating 95\% credible intervals for $\lambda$ (see the function ``credible\_interval" in \emph{Appendix S2}). The 95\% credible interval for hypothetical galler-natural enemy pairs, meanwhile, widened from (0.00001, 0.008) to (0.0005, 0.304).

@@

      Rather than calculating credible intervals for a posterior distribution after collecting data, we may wish to know how many data points are necessary to obtain a given level of confidence that two co-occurring species do not interact. The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact (Fig.~\ref{Salix_pdfs_cdfs}; see function samples\_for\_threshold in~\emph{Appendix S3}). The number of samples required to be 95\% confident that the interaction probability between galler and natural enemy species is below a threshold increases quickly as the threshold decreases (\emph{Appendix S5}). The 95\% credible interval is (\textless0.001, 0.303) for the probability of interaction between two species observed to co-occur but never interact. To be 95\% confident that the probability of interaction is below 0.1, 0.05, or 0.01 would require 15, 39, and 229 observed co-occurrences, respectively.

@@

    It is straightforward to compute most network metrics when the different $\lambda$ of the adjacency matrix are known and assumed not to vary~\citep{Poisot2016}. Incorporating variance in $\lambda$ into these calculations, however, is not so easy. Computation of these metrics involves non-linear functions, and Jensen's inequality states that the average of a non-linear function of a stochastic variable differs from the function of the average of that variable. Any uncertainty in the values of $\lambda$ could therefore bias both the mean and variance of a network metric. One way to avoid potentially biased analytical calculation of network properties is to calculate the properties of a suite of simulated networks.

    Using the prior distributions and procedures described above, we calculated posterior probability distributions for species pairs that were not observed interacting. Using these posterior distributions and assuming probabilities of 1 for pairs of species that were observed interacting, we created a suite of 100 webs by randomly sampling from each posterior distribution. After obtaining these posterior networks, we calculated the connectance of each web, as well as the mean number of links per galler and per natural enemy, and the nestedness (NODF) of the network. To demonstrate how these network metrics will be affected by detection uncertainty, we then created a suite of filtered networks for each posterior network. Networks were filtered by randomly sampling 99\%, 95\%, 90\%, 80\%, 70\%, 60\%, and 50\% of the interactions included in each posterior network. This gradient is akin to a gradient of sampling effort. For each level of detection accuracy, we created 100 randomly-sampled networks per posterior-probability network (giving 100 posterior networks and 1000 detection-filtered networks). We calculated the same network properties as described above for all posterior and detection-filtered networks.

    We found that the connectance, mean links per galler, and mean links per natural enemy were much lower in the observed web (C=0.078, $L_{galler}$=9.99, and $L_{natural enemy}$=7.45, respectively) than in the posterior webs (0.186 $\leq$ C $\leq$ 0.198, 13.4 $\leq L_{galler} \leq$ 14.6, and 23.4 $\leq L_{natural enemy} \leq$ 25.0). When the detection probability was relatively low (i.e., 50\%), however, the properties of randomised networks became similar to those in the observed webs (Fig.~\ref{posterior_webs}A,B,D). Nestedness was higher in the observed network (NODF=6.85) than in the posterior webs (6.31 $\leq NODF \leq$ 6.82; Fig.~\ref{posterior_webs}C); in this case, the stronger the detection filter the farther apart were the observed and posterior webs.

@@

\begin{fullbox}{}
  \begin{spacing}{1.0}
    \textbf{Box 1: }\emph{Salix}-galler-natural enemy dataset.\\
    \indent As a case study, we use an extensively sampled \emph{Salix}-galler-natural enemy meta-network. This dataset consists of a single community type sampled across Europe: willow (\emph{Salix}) species, willow-galling sawflies, and their natural enemies. The data were collected over 29 years at 374 unique locations across Europe. The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes. The high spatiotemporal resolution of this network and the unusually high sampling effort implemented at the site level makes this dataset particularly well suited for illustrating the difficulties in completely sampling a network and testing Bayesian approaches to overcome these difficulties.\\
    \indent We may begin by comparing the frequencies of co-occurrences and interactions to reveal the challenge of having sufficient sampling to be confident that an interaction does not occur. Most pairs of species (9,794/12,096 galler-natural enemy pairs) are never found co-occurring and, for species that did occur together, the total number of co-occurrences was generally low (mean=3.87, variance=28.8; Fig.~\ref{histograms}A). The bulk of these co-occurring species pairs were never observed to interact: only 7.76\% of galler-natural enemy pairs were observed interacting. Of those pairs that did interact, the incidence of interaction was also low (mean=4.04, variance=29.3; Fig.~\ref{histograms}B). Thus, even in the most extensive data set that we could find, there was very little empirical data for each species pair. This suggests that limited sampling is a major source of uncertainty in all empirical networks. This dataset also illustrates the potential for increased sampling to not necessarily reveal more interactions as a pair of species that is able to interact may not be observed interacting in all samples where the pair co-occurs (Fig.~\ref{histograms}C).
  \end{spacing}
\end{fullbox}

@@

  \begin{figure}[h!]
      \caption{Despite the high levels of replicaiton in our example dataset, most galler-natural enemy pairs were never observed co-occurring, and those that did co-occur were rarely observed interacting. \textbf{A)} Here we show a histogram of the number of pairs of species observed co-occurring at least once; the 9794 galler-enemy pairs that were never observed co-occurring are omitted.
      \textbf{B)} Here we show a histogram of the number of observed interactions within pairs of co-occurring species. Species which co-occurred but never interacted are included. 
      \textbf{C)} Here we show, for each species pair, the number of observed interactions plotted against the number of observed co-occurrences. The red, dashed line indicates a 1:1 relationship between interactions and co-occurrences.}
      \label{histograms}
      \begin{center}
      \includegraphics*[height=.6\textheight]{figures/GP_histogram.eps}
      \end{center}
      \end{figure}

  \begin{figure}[h!]
    \caption{Imperfect detection of interactions has a strong effect on the number of samples required to be confident that an interaction does not occur. Assume that we want to infer the probability of an interaction between two species, $i$ and $j$ and that this interaction is completely impossible (i.e. the true $\lambda=0$). When estimating $\lambda$, the number of observed interactions will follow a binomial distribution with number of interactions $k$ and number of observations $n$. Using this distribution, we can compute the credible interval of the estimated probability $\lambda$. A single observation of species co-occurrence reveals very little regarding the probability of the interaction as the credible interval for a pair of species with one observation essentially spans from 0 to 1. Only with 35 observations will the upper limit of the credible interval be lowered to 0.1 (dashed, red line). Thus, adding more observations is useful in controlling uncertainty, but the number of observations added needs to be very high. Here we show the upper bound (solid black line) of a 95\% Clopper-Pearson true credible interval for $\lambda$ when $k=0$ ($i$ and $j$ have not been observed interacting) for a variety of $n$. A threshold interaction probability of 0.1 is indicated by the dashed red line. }
    \label{upper_limits}
    \begin{center}
    \includegraphics*[width=.8\textwidth]{figures/upper_limit_DG.eps}
    \end{center}
    \end{figure}

  \begin{figure}[h!]
    \caption{Using prior distributions based on the galler-natural enemy network sampled at a single site in~\citet{Kopelke2017}, we calculate posterior distributions for the probability of interaction ($\lambda$) between two species that have not yet been observed interacting ($k = 0$). 
    Posterior distributions for $\lambda$ narrow and approach zero as the number of observed co-occurrences ($n$) increases. Likewise, the maximum likelihood estimator for the mean probability of interaction (diamonds at top of each panel) approaches zero and the 95\% credible interval (lines at top of each panel) narrows as sample size increases.
    Dashed lines indicate threshold probabilities of 0.01, 0.05, and 0.1. The number of samples required to obtain a 95\% credible interval below each threshold increases rapidly. It takes just over 20 observed co-occurrences to be 95\% confident that $\lambda<0.10$, approximately 50 co-occurrences to be 95\% confident that $\lambda<0.05$, and over 100 co-occurrences to be 95\% confident that $\lambda<0.01$. Increasing the desired confidence level will also increase the number of samples required.
    }
    \label{Salix_pdfs_cdfs}
    \begin{center}
    \includegraphics*[width=.8\textwidth]{figures/GP_pdfs_increasing_N_Zillis.eps}
    \end{center}
    \end{figure}
